Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-03 vertical-thermal-review_SI.Rmd
reinstate note
issue #58

>>>>

*Note on interpreting $T_{veg}$*:

Vegetation temperature ($T_{veg}$) is measured using infrared sensors that integrate across both leaves and woody vegetation. 
Leaf and branch temperatures often differ substantially; for instance, exposed tropical tree bark can be much warmer than leaves [@pauTropicalForestTemperature2018; @stillImagingCanopyTemperature2021; @johnstonWhatLiesVertical2020].
Thus, vegetation temperature ($T_{veg}$) does not always equal or approximate $T_{leaf}$, particularly in settings where leaf area is low relative to woody vegetation (i.e., low-LAI ecosystems and understories).
